---
documentclass: article
author: "Rishabh Jain, Chengyu Wu, Yunhan Xu, Wei Xiao, George Zhang, Yingzhe Jin"
header-includes:
   \usepackage[letterpaper, margin=1in]{geometry}
   \usepackage{fancyhdr}
   \pagestyle{fancy}
   \lhead{19819 A/B Testing, Design, and Implementation}
   \rhead{Fall 2021}
   \cfoot{Page \thepage}
   \renewcommand{\footrulewidth}{0.4pt}
   \fancypagestyle{plain}{\pagestyle{fancy}}
   \title{\textbf{Will offering a feature-by-feature comparison table encourage customers to opt for the premium plan?}}
output: pdf_document
# output: html_document
---

```{=latex}
\maketitle
```

```{r include=FALSE}
# Load libraries
library(data.table)
library(stargazer)
library(pwr)
library(plm)
library(dplyr)
library(ggplot2)
library(egg)
library(car)

# Clear workspace
# rm(list=ls())
# theme_set(theme_article())
```

```{r include=FALSE}
###Data cleaning and preparation

# Load data
surveyData = fread("survey_data.csv", verbose = FALSE)

# Remove first 2 rows and not required columns
surveyData = surveyData[-c(1:2), ]

# Renaming columns
colnames(surveyData) = c("tableResponse", "listResponse", "gender", "age", "income", "monthExpense",
                         "profWorker", "employerBill", "streamingService", "streamingPayment",
                         "phoneOS", "noWifiHrs")

# Add treatment indicator (column name: treatment)
# This is the 'treatment in experiment' / x in regression
surveyData = surveyData %>%
   mutate(treatment = ifelse(tableResponse != "", 1, 0))

# Column for final response (column name: response)
# This is the 'outcome of interest' / y in regression
# Answers the question: How likely are you to opt for the premium plan
surveyData = surveyData %>%
   mutate(response = ifelse(tableResponse != "", tableResponse, listResponse))

# Converting columns to factor
surveyData$gender = factor(surveyData$gender)
surveyData$age = factor(surveyData$age, 
                        levels = c("18-24","25-29","30-39","40+"))
surveyData$income = factor(surveyData$income,
                           levels = c("$0 - $25,000", "$25,000 - $50,000", "$50,000 - $75,000",
                              "$75,000 - $100,000", ">$100,000"))
surveyData$monthExpense = factor(surveyData$monthExpense,
                                 levels = c("$0 - $1,000", "$1,000 - $2,000", "$2,000 - $3,000",
                                    "$3,000 - $4,000", ">$4,000"))
surveyData$profWorker = factor(surveyData$profWorker)
surveyData$employerBill = factor(surveyData$employerBill)
surveyData$streamingService = factor(surveyData$streamingService)
surveyData$streamingPayment = factor(surveyData$streamingPayment,
                                     levels = c("", "$100 - $150", "$150 - $200", "$50 - $100", "0 - $50",
                                        ">$200"))
surveyData$phoneOS = factor(surveyData$phoneOS)
surveyData$noWifiHrs = factor(surveyData$noWifiHrs,
                              levels = c("0 - 3 hours", "3 - 6 hours", "6 - 10 hours", "10 - 15 hours", "> 15 hours"))
surveyData$treatment = factor(surveyData$treatment)
surveyData$response = factor(surveyData$response,
                            levels = c("0 - Not likely at all", "1 - Probably not", "2 - Somewhat not likely",
                                       "3 - Somewhat likely", "4 - Highly likely", "5 - I will surely take the plan"))

# Convert response variable to numeric
surveyData <- surveyData %>%
  mutate(response_numeric = ifelse(response == "5 - I will surely take the plan",5, 
                                   ifelse(response == "4 - Highly likely", 4, 
                                          ifelse(response == "3 - Somewhat likely", 3, 
                                                 ifelse(response == "2 - Somewhat not likely", 2, 
                                                        ifelse(response == "1 - Probably not", 1, 
                                                               ifelse(response == "0 - Not likely at all", 0, NA)))))))
```

## 1. Executive Summary
Nowadays, online payment methods are becoming more and more mature. People more or less need to perform some payment behaviors online to meet their daily needs, such as subscribing to members, upgrading premium accounts, and paying for packages. There are various online payment and promotion methods. For merchants, differentiated pricing is an important way to divide customer groups and obtain higher profits. Compared with telephone or oral promotion, a major advantage of web promotion is that it can clearly list the advantages of various paid packages and the content covered, making it easier for users to consume on demand, and it is also easier for users to perceive the implicit Demand drives them to consume more advanced plans.
In web promotion, we often see that different plans are covered in a highly visible table-forms to promote the functions that these plans can achieve from different aspects. There are also some web pages that just list the functions of different plans, but they are usually a long string of obscure text or comments. We are trying to explore whether the use of visual tables will promote users' desire to buy, and through clear comparison, whether users will be more likely to choose advanced plans.
## 2. Experimental Design
Our experimental questionnaire will consist of two parts. The first part is the main A/B test problem, which is to provide the same information to the user but the way it is presented is different. It is distinguished by means of visual tables and large paragraphs of text. The second part is the user division problem, which mainly asks questions related to user characteristics, so as to facilitate randomization of user groups.

Evaluation Metrics
Compared to the standard plan, how likely is it that you will opt for the premium plan?
Range from 0 to 5
0 - Not likely at all
1 - Probably not
2 - Somewhat not likely 
3 - Somewhat likely 
4 - Highly likely 
5 - I will surely take the plan


Survey Questions (Control Variables)
Age
Gender
Income (in bracket ranges)
Are you employed / working professional?
Does your employer pay for the plan?
Which country are you from?
Do you have any experience with online subscriptions before? If so, how much on avg /month?
Do you use iOS or Android?
How many family members do you have in your household?
On average, how many hours per day you don’t have access to wifi?
Question for proxy of spending habit


## 3. Descriptive Statistical Analysis

```{r include=FALSE}
# Separating treated and un-treated data
treatedData = surveyData[which(surveyData$treatment == 1)]
untreatedData = surveyData[which(surveyData$treatment == 0)]

### Descriptive Statistical Analysis

# Performing non-parametric independent sample t-test (Mann-Whitney Test)
# Performed to test if treated and untreated groups are alike

MWTestResult = data.frame(parameter = character(), pvalue = numeric())

# Gender
testResult = wilcox.test(as.numeric(treatedData$gender),
                         as.numeric(untreatedData$gender))
pValue = testResult$p.value
row = c("gender", pValue)
MWTestResult = rbind(MWTestResult, row)

# Age
testResult = wilcox.test(as.numeric(treatedData$age),
                         as.numeric(untreatedData$age))
pValue = testResult$p.value
row = c("age", pValue)
MWTestResult = rbind(MWTestResult, row)

# Income
testResult = wilcox.test(as.numeric(treatedData$income),
                         as.numeric(untreatedData$income))
pValue = testResult$p.value
row = c("income", pValue)
MWTestResult = rbind(MWTestResult, row)

# Monthly Expense
testResult = wilcox.test(as.numeric(treatedData$monthExpense),
                         as.numeric(untreatedData$monthExpense))
pValue = testResult$p.value
row = c("monthExpense", pValue)
MWTestResult = rbind(MWTestResult, row)

# Professional Worker
testResult = wilcox.test(as.numeric(treatedData$profWorker),
                         as.numeric(untreatedData$profWorker))
pValue = testResult$p.value
row = c("profWorker", pValue)
MWTestResult = rbind(MWTestResult, row)

# Streaming Service
testResult = wilcox.test(as.numeric(treatedData$streamingService),
                         as.numeric(untreatedData$streamingService))
pValue = testResult$p.value
row = c("streamingService", pValue)
MWTestResult = rbind(MWTestResult, row)

# Phone OS
testResult = wilcox.test(as.numeric(treatedData$phoneOS),
                         as.numeric(untreatedData$phoneOS))
pValue = testResult$p.value
row = c("phoneOS", pValue)
MWTestResult = rbind(MWTestResult, row)

# No Wifi Hrs
testResult = wilcox.test(as.numeric(treatedData$noWifiHrs),
                         as.numeric(untreatedData$noWifiHrs))
pValue = testResult$p.value
row = c("noWifiHrs", pValue)
MWTestResult = rbind(MWTestResult, row)

colnames(MWTestResult) = c("parameter", "pvalue")

MWTestResult['pvalue'] = lapply(MWTestResult['pvalue'], as.numeric)
MWTestResult['pvalue'] = round(MWTestResult['pvalue'], 3)
MWTestResult = MWTestResult[order(MWTestResult$pvalue), ]
MWTestResult['Are the groups same?'] = ifelse(MWTestResult$pvalue > 0.05, TRUE, FALSE)
```

Number of observations in treated set: `r nrow(treatedData)`

Number of observations in untreated set: `r nrow(untreatedData)`

```{r echo=FALSE, results='asis'}
stargazer(MWTestResult[],
          type = 'latex',
          header = FALSE,
          summary = FALSE,
          rownames = FALSE,
          title = "Mann-Whitney Test Results
          (Non-Parametric equivalent of independent samples t-test)")
```

```{r, include=FALSE}
### Descriptive Statistical Analysis Visualizations

# Gender
ggplot(surveyData, aes(x = gender, group = 1)) +
   geom_bar(aes(y = ..prop..), stat = 'count', fill = "lightblue") +
   scale_y_continuous(labels = scales::percent_format()) +
   facet_grid(~ treatment) +
   theme(axis.text.x = element_text(angle = 90)) +
   labs(title = "Gender distribution in treated and untreated group",
        caption = "*0 means untreated and 1 means treated")
```

```{r, include=FALSE}
# Age
ggplot(surveyData, aes(x = age, group = 1)) +
   geom_bar(aes(y = ..prop..), stat = 'count', fill = "lightblue") +
   scale_y_continuous(labels = scales::percent_format()) +
   facet_grid(~ treatment) +
   labs(title = "Age distribution in treated and untreated group",
        caption = "*0 means untreated and 1 means treated")
```


```{r}
# Income
ggplot(surveyData, aes(x = income, group = 1)) +
   geom_bar(aes(y = ..prop..), stat = 'count', fill = "lightblue") +
   scale_y_continuous(labels = scales::percent_format()) +
   facet_grid(~ treatment) +
   theme(axis.text.x = element_text(angle = 90)) +
   labs(title = "Income distribution in treated and untreated group",
        caption = "*0 means untreated and 1 means treated")
```


```{r, include=FALSE}

# Monthly Expense
ggplot(surveyData, aes(x = monthExpense, group = 1)) +
   geom_bar(aes(y = ..prop..), stat = 'count', fill = "lightblue") +
   scale_y_continuous(labels = scales::percent_format()) +
   facet_grid(~ treatment) +
   theme(axis.text.x = element_text(angle = 90)) +
   labs(title = "Distribution of monthly expenses in treated and untreated group",
        caption = "*0 means untreated and 1 means treated
        ** Expenses are beside mortagage / rent")
```


```{r, include=FALSE}
# Professionally Employed
ggplot(surveyData, aes(x = profWorker, group = 1)) +
   geom_bar(aes(y = ..prop..), stat = 'count', fill = "lightblue") +
   scale_y_continuous(labels = scales::percent_format()) +
   facet_grid(~ treatment) +
   labs(title = "Distribution of professional workers in treated and untreated group",
        caption = "*0 means untreated and 1 means treated")
```


```{r}
# Streaming Service Subscribers
ggplot(surveyData, aes(x = streamingService, group = 1)) +
   geom_bar(aes(y = ..prop..), stat = 'count', fill = "lightblue") +
   scale_y_continuous(labels = scales::percent_format()) +
   facet_grid(~ treatment) +
   labs(title = "Distribution of streaming service subscribers in treated and untreated group",
        caption = "*0 means untreated and 1 means treated")
```


```{r, include=FALSE}
# Mobile OS
ggplot(surveyData, aes(x = phoneOS, group = 1)) +
   geom_bar(aes(y = ..prop..), stat = 'count', fill = "lightblue") +
   scale_y_continuous(labels = scales::percent_format()) +
   facet_grid(~ treatment) +
   labs(title = "iOS/Android users' distribution in treated and untreated group",
        caption = "*0 means untreated and 1 means treated")
```


```{r, include=FALSE}
# No Wifi Hours
ggplot(surveyData, aes(x = noWifiHrs, group = 1)) +
   geom_bar(aes(y = ..prop..), stat = 'count', fill = "lightblue") +
   scale_y_continuous(labels = scales::percent_format()) +
   theme(axis.text.x = element_text(angle = 90)) +
   facet_grid(~ treatment) +
   labs(title = "Distribution of No-Wifi-Hrs in treated and untreated group",
        caption = "*0 means untreated and 1 means treated")
```

## 4. Causal Effect Analysis

```{r}
surveyData
```

From the statistical test above, we can see that there is no significant difference in population characteristics between the treatment and control group so that the experiment is ideally randomized. In this section, we will study the causal effect of our treatment, the table format of presenting products, on the customers' likelihood of buying the premium one. 

We perform a T-test between the willingness to pay of the treatment and control groups. From the result, we can see that the mean response for the treatment group (table format) is lower than that for the control group (paragraph format) and the difference between the two means is statistically significant at the 0.001 significance level. We may infer that the table format of presenting the product significantly brings down the customers' willingness to pay for the premium option than the paragraph format. 

```{r}
t.test(surveyData$response_numeric ~ surveyData$treatment)
```

The box plot below demonstrates the distribution of the response (willingness to pay for the premium plan) from the control and treatment groups. We can see that most control group participants responded with a relatively positive answer, with most of them selecting 3 (somewhat likely) or higher; on the contrary, the treatment group participants responded with a relatively calm answer, while 50% (median) of the customers selected "likely" of different extent, a significant number of them in the treatment group selected "unlikely" or even "very unlikely" response. 

```{r}
surveyData %>%
  ggplot(aes(x = treatment, y = response_numeric)) +
  geom_boxplot()
```



```{r}

lm_1 <- lm(response_numeric ~ treatment, data = surveyData)
lm_2 <- lm(response_numeric ~ treatment + gender + age + income + monthExpense + profWorker +
             streamingService + phoneOS + noWifiHrs, data = surveyData)

```

To further identify the treatment effect of the presenting format on the willingness to pay. We perform a series of regressions using the data we collected as below.

The first column represents a simple OLS regression model of the treatment on the outcome variable. While the estimated constant term represents the average outcome level -- the likelihood/willingness to pay for the premium plan, the coefficient of the treatment variable stands for the causal effect from the presenting format. We may infer that, on average, assuming the experiment is well randomized and all other factors controlled, the table format of presenting or comparing products may bring down the mean likelihood of purchasing by 0.414, measured in a 6-point continuous scale.

The second column is the OLS model, including all the control variables we collected from the participants. When controlling for more features between the two groups, we can still observe a significant gap between the likelihood of opting for the premium plan of the two groups.

We expect that the control variables distribute evenly between the two groups, and they should not demonstrate significant capability in explaining the variance in our outcome variable. But from the table, we can still observe that some coefficients are statistically significant, e.g. the dummy indicating more than \$100,000 annual income, the dummy indicating monthly expense between \$3,000 to \$4,000, the dummy indicating the subscription of streaming service, and the dummy indicating the daily time without WIFI between 10 to 15 hours. The significance of these coefficients means that these attributes are not randomly assigned to the two groups. There are still some underlying differences between the treatment and control group to identify the true causal effect.

```{r}
stargazer(lm_1, lm_2,
          title = "OLS Regression",
          type = "text",
          model.numbers = FALSE,
          omit = c(),
          covariate.labels = c("Treatment", "Male", "Non-binary Gender",
                               "Undeclared Gender", "Age 25-29", "Age 30-39",
                               "Age 40+", "Income $25k-$50k", "Income $50k-$75k",
                               "Income $75k-$100k", "Income $100k+", "Expense $1k-$2k",
                               "Expense $2k-$3k", "Expense $3k-$4k", "Expense $4k+",
                               "Professional", "Streaming Service", "iOS", "No Wifi 3h-6h",
                               "No Wifi 6h-10h", "No Wifi 10h-15h", "No Wifi 15h+", "Constant")
)
```

The treatment effects identified from the regression above reveal that the table format of presenting products brings negative effects on the customers' willingness to pay for the premium services, at least in our phone plan scenario, which is somewhat contradicting our original assumption that clearer comparison may nudge the customers to make a more premium choice. We guess that this phenomenon may be due to the following two reasons:

1. The table format helps customers to behave more rationally. The comparison table clearly lists the functional differences between the two services, enabling customers to compare price differences and feature differences between products more straightforwardly and quantitatively. The more complete the customer's understanding of product information, the more impulsive consumption behavior may be offset by rationality.

2. The standard and premium plan design in our scenario is unreasonable. When most of the functions of the two plans and the pricing strategies are determined arbitrarily, we may probably come up with two plans with inductive bias that comes from the consumption habits of the designers. Although we believe that the two plans should be equally attractive to customers, one of them may be the one more favored by the real-world users. In our case, the standard plan may seem more cost-effective so that when the information of the two plans is revealed more thoroughly, more customers may turn to the standard one.

In the next section, we study the heterogeneous effects. How does the treatment effect differ for different types of respondents?

```{r}
he_gender <- lm(response_numeric ~ treatment + gender + treatment:gender,
                data = surveyData)

he_age <- lm(response_numeric ~ treatment + age + treatment:age,
                data = surveyData)

he_income <- lm(response_numeric ~ treatment + income + treatment:income,
                data = surveyData)

he_expense <- lm(response_numeric ~ treatment + monthExpense + treatment:monthExpense,
                data = surveyData)

he_prof <- lm(response_numeric ~ treatment + profWorker + treatment:profWorker,
                data = surveyData)

he_streaming <- lm(response_numeric ~ treatment + streamingService + treatment:streamingService,
                data = surveyData)

he_os <- lm(response_numeric ~ treatment + phoneOS + treatment:phoneOS,
                data = surveyData)

he_wifi <- lm(response_numeric ~ treatment + noWifiHrs + treatment:noWifiHrs,
                data = surveyData)

```


```{r}
stargazer(he_gender, he_age,
          title = "OLS Regression",
          type = "text",
          model.numbers = FALSE,
          covariate.labels = c("Treatment", "Male", "Non-binary Gender",
                               "Undeclared Gender", "Treatment:Male", "Treatment:Non-binary", "Treatment:Undeclared",
                               "Age 25-29", "Age 30-39", "Age 40+", "Treatment:Age 25-29", 
                               "Treatment:Age 30-39", "Treatment:Age 40+", "Constant")
)
```

The treatment effect for males is less than that for females. On average, controlling for other factors, a table comparison of features is associated with 0.679 unit less likelihood of opting for the premium option for females, but only 0.178 unit less for males. 

The treatment effect doesn't vary by age group.


```{r}
stargazer(he_income, he_expense,
          title = "OLS Regression",
          type = "text",
          model.numbers = FALSE,
          covariate.labels = c("Treatment", "Income $25k-$50k", "Income $50k-$75k",
                               "Income $75k-$100k", "Income $100k+", "Treatment:Income $25k-$50k", 
                               "Treatment:Income $50k-$75k", "Treatment:Income $75k-$100k", "Treatment:Income $100k+",
                               "Expense $1k-$2k", "Expense $2k-$3k", "Expense $3k-$4k", "Expense $4k+",
                               "Treatment:Expense $1k-$2k", "Treatment:Expense $2k-$3k", 
                               "Treatment:Expense $3k-$4k", "Treatment:Expense $4k+", "Constant")
)
```

The treatment effect doesn't vary by income group or monthly expense group.

```{r}
stargazer(he_prof, he_streaming,
          title = "OLS Regression",
          type = "text",
          model.numbers = FALSE,
          covariate.labels = c("Treatment", "Professional", "Treatment:Professional",
                               "Streaming Service", "Treatment:Streaming Service",
                               "Constant")
)
```

This table shows the heterogeneous effect of covariate 'profworker' (whether they are professional workers) and the heterogeneous effect of covariate 'streamingService' (Whether they have streaming service). We could find that the two heterogeneous effect are both not statistically significant, which indicates that the treatment affect sub-groups similarly, in other words, this heterogeneous effect is similar across different sub-groups. 

```{r}
stargazer(he_os, he_wifi,
          title = "OLS Regression",
          type = "text",
          model.numbers = FALSE,
          covariate.labels = c("Treatment", "iOS", "Treatment:iOS", "No Wifi 3h-6h",
                               "No Wifi 6h-10h", "No Wifi 10h-15h", "No Wifi 15h+",
                               "Treatment:No Wifi 3h-6h", "Treatment:No Wifi 6h-10h", 
                               "Treatment:No Wifi 10h-15h", "Treatment:No Wifi 15h+",
                               "Constant")
)
```

This table shows the heterogeneous effect of covariate 'phoneOS' (cellphone operating system type) and the heterogeneous effect of covariate 'noWifiHrs' (the number of hours without wifi access). We could find that the heterogeneous effect of 'phoneOS' is not statistically significant, which indicates that the treatment affect sub-groups(people who use IOS, people who use Android) similarly. In other words, this heterogeneous effect is similar across different sub-groups of variable 'phoneOS'. 

However, the treatment effect for respondents who don't have access to WIFI for 10-15 hours is less than that for respondents who don't have access to WIFI for 0-3 hours. This makes sense, since people tend to buy premium (unlimited cellular data) when they have little access to WIFI. 

## 5. Results(I think this should be combined with part 4)

## 6. Conclusion
To sum up the above causal effect analysis, we conclude that table format of comparing products will potentially reduce the consumers’ desire to purchase premium products, which contradicts to our initial hypothesis. The accuracy of this experiment may suffer from relatively small sample. In the future analysis, we would like to collect more information from larger sample size to improve the analysis results. 
